Kimbee: A Speech Therapy Application For Children

### 2015-03-09 Paper/paper.tex
fixed

\subsection{Game ({\secit Kimbee})}
The Game or Kimbee system, see Figure \ref{fig:tech}, is the system that the children interact with to practice speech. Since this system also performs speech processing to determine speech correctness, there are many interacting components. From a high level, the major sub systems are: the {\em Phaser Game Implementation}, the {\em Speech Processing Component}, and the {\em Server Application Programming Interface (API)}. We target this project toward web technologies to allow wide distribution and adoption. From a design standpoint, we strived to make each system loosely connected and non-disruptive to gameplay. This required us to explore various new web technologies including HTML5 Web Workers for multithreading and the UserMedia HTML5 API.

@@

@@

\subsubsection{Component 1}

>>>>

\subsection{Game ({\secit Kimbee})}
The Game or Kimbee system, see Figure \ref{fig:tech}, is the system that the children interact with to practice speech. It is written in TypeScript and compiled to optimized JavaScript. Since this system also performs speech processing to determine speech correctness, there are many interacting components. From a high level, the major sub systems are: the {\em Phaser Game Implementation}, the {\em Speech Processing Component}, and the {\em Server Application Programming Interface (API)}. We target this project toward web technologies to allow wide distribution and adoption. From a design standpoint, we strived to make each system loosely connected and non-disruptive to gameplay. This required us to explore various new web technologies including HTML5 Web Workers for multithreading and the UserMedia HTML5 API.

@@

\subsection{Central Server}
The {\em Central Server}, see Figure \ref{fig:tech}, faciliates communication between all the {\em Kimbee Game} instances and the {\em Therapist Portal}. It is written in Node JS and stores data in a MongoDB instance. We also do audio encoding to create playable audio files from child microphone data obtained from {\em Kimbee Game} instances.

\subsubsection{Data Models}
  The server has three data models: recordings, children, and therapists. Recordings are the encoded microphone encodings and recognition data from the {\em Kimbee Game} instances. They are tied to a particular game instance via a unique token generated by the {\em Kimbee Game}. Children are models created by therapists to effectively ``hook into'' recordings. They specify a name for the child, and their token obtained from their {\em Kimbee Game} instance. Future recordings are then relayed to the therapist from this particular {\em Kimbee Game} instance. Finally, therapists are the authenticated user records that contain a user email and password and provides access into the therapist portal.

\subsubsection{Audio Encoding \& Recording Storage}
  When a audio file is recieved by a {\em Kimbee Game} instance, we encode it into a WAV file by interleaving the left and right buffer channels from the microphone. This file is then compressed and stored into the database as a recording. The recognition data (whether the {\em Kimbee Game} instance thinks the recording was correct) and the target word are also stored with the recording model.

\subsubsection{Therapist Portal Application Programming Interface}
  The server exposes a set of APIs for the {\em Therapist Portal} to utilize. This includes functionality to retrieve recordings for a particular child owned by the therapist record, retrieve the authenticated therapist record, authenticate therapists, and register therapists. This functionality is used via a HTTP interface with the {\em Central Server}.

@@
